### 2022-11-26 writeups/Observations.tex
fit type classifiers

{\bf \emph{Observations on the Datasets}} \hfill Nicolas Cloutier\\\\

@@

Since the model used distributions from the antisemitic tweet dataset, using these tweets for evaluation is not very useful. That being said, we can use it as a preliminary tool to make sure the model is identifying differences in word distributions. Testing the model on the all of the dataset tweets for the Boolean antisemitic classifications and the type classifications evaluated on only the antisemitic tweets for which classifications were provided, the following accuracy ratings (out of 1) were achieved.
\begin{center}
Table 1: Evaluation on training data\\
\begin{tabular}{ |c|c|c|c| } 
 \hline
{\bf Method} & \bf{Task} & \bf{Accuracy} & \bf{Chance Accuracy}\\
\hline
 Vector distance & Boolean classification & 0.76 & 0.5\\ 
 Vector distance & Type classification & 0.57 & 0.25\\ 
 Cosine similarity & Boolean classification & 0.76 & 0.5\\ 
 Cosine similarity & Type classification & 0.57 & 0.25\\ 
 \hline
\end{tabular}
\end{center}

It would appear as if the method used has little effect on the accuracy, and that the models, scoring significantly above chance, have at the very least identified distribution differences in the tweets. The model can be used for binary classification on the 4Chan posts and normal tweets (a series of several thousand tweets randomly gathered from Twitter tweeted over the course of 2021) to check that they correctly identify that the 4Chan posts are mostly antisemitic and the normal tweets are mostly not antisemitic. Results of the model on those datasets are shown below. In Table 2, the ``Bool. avg.'' column is the arithmetic mean of all of the Boolean classifications of each dataset, the ``Cos. Bool. avg.'' column is the same but using cosine similarity, and the columns ending in ``\#'' give the raw number of occurences of each type classification for each post in the dataset (using vector distance).
\begin{center}
Table 2: Data summaries\\
\begin{tabular}{ |c|c|c|c|c|c|c|}
\hline {\bf Dataset} & {\bf Bool. avg.} & {\bf Cos. Bool. avg.} & {\bf 1 \#} & {\bf 2 \#} & {\bf 3 \#} & {\bf 4 \#}\\
\hline 
4Chan data & 0.85 & 0.85 & 504 & 575 & 1474 & 793\\
Normal tweets & 0.60 & 0.60 & 3675 & 1357 & 2419 & 3549\\
Labeled data & 0.44 & 0.44 & 515 & 133 & 277 & 296\\
\hline
\end{tabular}
\end{center}

Again, the different methods for calculating similarity appear to not affect outcomes at all. The occurence columns are given with vector distance, but these data are exactly the same as those calculated using cosine similarity. Looking at the Boolean averages for the normal data, it appears to be higher than may have been anticipated or hoped for, given that the tweets were collected from a random sample of tweets across 2021. Interestingly, the Boolean average of the normal tweets is higher than the Boolean average of the labeled data, which contained antisemitic tweets.
\end{document}

>>>>

{\bf \emph{Data Science Techniques for Automatic Antisemitism Detection}} \hfill Nicolas Cloutier

Last edited \today.\\

@@

Since the model used distributions from the antisemitic tweet dataset, using these tweets for evaluation is not very useful. That being said, we can use it as a preliminary tool to make sure the model is identifying differences in word distributions. Testing the model on the all of the dataset tweets for the Boolean antisemitic classifications and the type classifications evaluated on only the antisemitic tweets for which classifications were provided, the following accuracy ratings (out of 1) were achieved.
\begin{center}
Table 1: Evaluation on training data\\
\begin{tabular}{ |c|c|c|c| } 
 \hline
{\bf Method} & \bf{Task} & \bf{Accuracy} & \bf{Chance Accuracy}\\
\hline Vector distance & Boolean classification & 0.76 & 0.5\\ 
\hline Vector distance & Type classification & 0.57 & 0.25\\ 
\hline Cosine similarity & Boolean classification & 0.76 & 0.5\\ 
\hline Cosine similarity & Type classification & 0.57 & 0.25\\ 
 \hline
\end{tabular}
\end{center}

It would appear as if the method used has little effect on the accuracy, and that the models, scoring significantly above chance, have at the very least identified distribution differences in the tweets. The model can be used for binary classification on the 4Chan posts and normal tweets (a series of several thousand tweets randomly gathered from Twitter tweeted over the course of 2021) to check that they correctly identify that the 4Chan posts are mostly antisemitic and the normal tweets are mostly not antisemitic. Results of the model on those datasets are shown below. In Table 2, the ``Bool. avg.'' column is the arithmetic mean of all of the Boolean classifications of each dataset, the ``Cos. Bool. avg.'' column is the same but using cosine similarity, and the columns ending in ``\#'' give the raw number of occurences of each type classification for each post in the dataset (using vector distance).
\begin{center}
Table 2: Data summaries\\
\begin{tabular}{ |c|c|c|c|c|c|c|}
\hline {\bf Dataset} & {\bf Bool. avg.} & {\bf Cos. Bool. avg.} & {\bf 1 \#} & {\bf 2 \#} & {\bf 3 \#} & {\bf 4 \#}\\
\hline 4Chan data & 0.85 & 0.85 & 504 & 575 & 1474 & 793\\
\hline Normal tweets & 0.60 & 0.60 & 3675 & 1357 & 2419 & 3549\\
\hline Labeled data & 0.44 & 0.44 & 515 & 133 & 277 & 296\\
\hline
\end{tabular}
\end{center}

Again, the different methods for calculating similarity appear to not affect outcomes at all. The occurence columns are given with vector distance, but these data are exactly the same as those calculated using cosine similarity. Looking at the Boolean averages for the normal data, it appears to be higher than may have been anticipated or hoped for, given that the tweets were collected from a random sample of tweets across 2021. Interestingly, the Boolean average of the normal tweets is higher than the Boolean average of the labeled data, which contained antisemitic tweets.\\

{\bf Machine Learning Models}

Three machine learning models were used: SVMs, Decision Trees, and Naïve Bayes classifiers. Each of those models was used for Boolean and type classification and with three seperate text representations (Bag-of-Words, raw frequency, and TF-IDF), making a total of 12 models. For the sake of evaluation, the rules-based model was retrained on only the training data, then tested on the test data. Models labeled RB are rules-based. The scores represent the proportion of the test dataset that the model correctly predicted, 1 means perfect predictions, 0 means entirely incorrect predictions.
\begin{center}
Table 3: Machine learning model evaluations and comparisons to rules-based model
\begin{tabular}{ |c|c|c|c| }
\hline {\bf Model type} & {\bf Text representation} & {\bf Boolean score} & {\bf Type score} \\
\hline Decision Tree & BoW & 0.653 &  0.513\\
\hline Decision Tree & Frequency & 0.695  &  0.692\\
\hline Decision Tree & TF-IDF & 0.703 & 0.487\\
\hline SVM & BoW & 0.703 & 0.692\\
\hline SVM & Frequency & 0.703 & 0.564\\
\hline SVM & TF-IDF & 0.678 & 0.462\\
\hline Naïve Bayes & BoW & 0.669 & 0.769\\
\hline Naïve Bayes & Frequency & 0.602 & 0.487\\
\hline Naïve Bayes & TF-IDF & 0.602 & 0.462\\
\hline Cosine Similarity (RB) & Frequency & 0.602 & 0.462\\
\hline Vector Distance (RB) & Frequency & 0.602 & 0.462\\
\hline
\end{tabular}
\end{center}
\end{document}
